---
title: "Unit 3: More"
format:
  html:
    code-fold: show
    code-tools: true
    include-before-body:
     - file: macros.md
  pdf: 
    include-before-body:
     - file: macros.tex
---

This is an example of using qmd as the source document with pdf as one target. I've taken out the qmd stuff that doesn't seem to render to pdf.



## LaTeX

$$
\theta = \int_0^\infty f(x,\theta)d\theta
$$

## LaTeX macro

> **Warning**: need to look back at this as having `include-before-body` in the yaml causes extra space at top of page.

$$
A = X \trans Y
$$




## Examples

```{r}
#| output: false
library(tidyverse)
library(gridExtra)
library(car)

options(repr.plot.width = 15, repr.plot.height = 8, repr.plot.res = 300)
```

### Spotify

This data consists of 30,000 Songs from the Spotify API with black-box machine 
learning quantifications of musical features.  There's no reason to think
they are a meaningful representative sample of any population of interest,
and we don't really know how the features are generated.

Still, this arguably doesn't prevent it from being interesting.

Downloaded from [https://www.kaggle.com/datasets/joebeachcapital/30000-spotify-songs](https://www.kaggle.com/datasets/joebeachcapital/30000-spotify-songs)


```{r}
#| output: true
spotify_df <- read.csv("../datasets/spotify_songs.csv")
print(summary(spotify_df))
```

Let's plot the popularity and danceability.

```{r}
grid.arrange(
    qplot(x=track_popularity, geom="histogram", data=spotify_df),
    qplot(x=log10(track_popularity), geom="histogram", data=spotify_df), ncol=2)
```



```{r}
ggplot(spotify_df) + geom_point(aes(y=track_popularity, x=danceability))
```


```{r}
ggplot(spotify_df) + geom_density_2d_filled(aes(y=track_popularity, x=danceability))
```


```{r}
names(spotify_df)
vars <- c("danceability", "energy", "key", "loudness", "speechiness", "acousticness", "instrumentalness", "liveness")
stopifnot(all(vars %in% names(spotify_df)))
```
